Understanding the Data Duplication in VM Cloud Storage

### 2012-03-13 data_analysis/main.tex
update
initial version

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{Understanding the Data Duplication of VM Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{
Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$, 
   {\normalsize $^\star$UC Santa Barbara}\\
   {\normalsize$^\dagger$Alibaba.com}
}
\date{}
\maketitle

%\input{abs}
%\input{intro} %introduce the vm cloud, snapshot
\input{overall} %complete dedup on both datasets 
\input{locality} %
\input{user.tex}
\input{scale}
\input{count} %data study, zipf, model of cds size and dedup efficiency
%\input{results}
%\input{related}
%\input{conclusion}
%\input{con}

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{dedup,dedup1}
}
\end{document}

>>>>

\begin{document}
%\title{Selective Deduplication for VM Snapshots in Cloud Storage}
\title{Understanding the Data Duplication in VM Cloud Storage}
%\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{
Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$\\
   {\normalsize $^\star$UC Santa Barbara, \{wei, tyang\}@cs.ucsb.edu}\\
   {\normalsize$^\dagger$Alibaba.com, \{hongtang, haojiang\}@alibaba.com}
}
\date{}
\maketitle

\input{abs}
\input{intro} %introduce the vm cloud, snapshot
\input{overall} %complete dedup on both datasets 
\input{locality} %
\input{user}
\input{dup}
%\input{count} %data study, zipf, model of cds size and dedup efficiency
%\input{results}
%\input{related}
%\input{conclusion}
\input{con}

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{dedup1,library}
}
\end{document}

### 2012-03-13 data_analysis/overall.tex
initial version

Table~\ref{tab:dedup} shows the data reduction of both methods, 
the reduction ratio is defined as the original size divide by size after reduction.
In general, complete deduplication achieves great data reduction

We see that

@@

\emph{Observation 2: Locality could be ruined with system upgrade.}
We notice dirty page method works poorly on CentOS, while complete deduplication works as efficient as on
other OSes. We believe this is probably due to the user have upgraded his system heavily during our
data sampling period, thus damaged the offset-based locality. In addition, the cloud will only have
more and more variations of operating systems with different installation configurations,
All these suggest data reduction base on offset may not work across different user snapshot backups.

>>>>

Table~\ref{tab:dedup} shows the data reduction of both methods, 
the reduction ratio is defined as the original size divide by size after reduction.
In general, complete deduplication achieves great data reduction, except for DDS data set.

@@

\emph{Observation 2: Locality could be damaged with system upgrade.}
We notice dirty page method works poorly on CentOS, while complete deduplication works as efficient as on
other OSes. We believe this is probably due to the user have upgraded his system heavily during our
data sampling period, thus damaged the offset-based locality. In addition, the cloud will only have
more and more variations of operating systems with different installation configurations,
All these suggest data reduction base on offset may not work across different user snapshot backups.

### 2012-03-13 data_analysis/user.tex
initial version

\section{Duplication V.S. Scale}
Dealing with large scale VM cloud, one of the most important questions is
whether data duplication will grow with the system scale. 
One hypothesis we have is that when the total number of block increases,
the chance that it being duplicated with another is going to be higher. Thus
we shall get better data reduction with larger scale of data.
Past study\cite{keren08} has suggested that virtual disks with 
operating systems installed should share large amount of software related data,
which indirectly supports this argument.
However, some other data study\cite{middleware11} showed the opposite.

@@

\begin{figure}
  \centering
  \epsfig{file=dedup_ratio.eps, width=3.2in}
  \caption{Reduction ratio of complete deduplication at different scale}
  \label{fig:scale}
\end{figure}

\emph{Observation 7: Reduction ratio by complete deduplication does not appear to increase with storage scale.}
In general we see almost no increment of reduction ratio along with the data scale, especially
for user generated data, shown as DDS in Figure\ref{fig:scale}, its reduction ratio is always
near 2:1. For OS disks, some Windows distributions appear to have incremental reduction, which is suspected to
because the size of Windows system is much bigger than Linux, thus it has much more redundant
data that widely exist in all VMs. We expect to perform larger scale study on OS disks in future
to obtain better conclusion on this topic.

>>>>

\section{Duplication V.S. Scale}
Dealing with large scale VM cloud, one of the most important questions is
whether data duplication will grow with the system scale. 
One hypothesis we have is that when the total number of block increases,
the chance that it being duplicated with another is going to be higher. Thus
we shall get better data reduction with larger scale of data.
Past study\cite{Jin2009} has suggested that virtual disks with 
operating systems installed should share large amount of software related data,
which indirectly supports this argument.
However, some other data study\cite{Jayaram2011} showed the opposite.

@@

\begin{figure}
  \centering
  %\epsfig{file=dedup_ratio.eps, width=3.2in}
  \includegraphics[width=3in,height=2in]{dedup_ratio.png}
  \caption{Reduction ratio of complete deduplication at different scale}
  \label{fig:scale}
\end{figure}

\emph{Observation 7: Reduction ratio by complete deduplication does not appear to increase.}
In general we see almost no increment of reduction ratio along with the data scale, especially
for user generated data, shown as DDS in Figure~\ref{fig:scale}, its reduction ratio is always
near 2:1. For OS disks, some Windows distributions appear to have incremental reduction, which is suspected to
because the size of Windows system is much bigger than Linux, thus it has much more redundant
data that widely exist in all VMs. We suspect the operating system and software related data
will occupy a significant percentage of data reduction regardless of number of VMs, will 
be studied in the next section.
%We expect to perform larger scale study on OS disks in future to obtain better conclusion on this topic.
